---
output:
  html_document:
    toc: no
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Global Variables, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y))
not_all_na <- function(x) any(!is.na(x))
not_any_na <- function(x) all(!is.na(x))

```


```{r Connect to Data Source, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")

conn3 <- dbConnect(odbc(),
                    Driver = "SQLServer",
                    # Server = "10.2.42.69", # old server
                    Server = "datahub-synapse.sql.azuresynapse.net",
                    database = "datahub_epic_dw",
                    UID = "MSS_USER",
                    PWD = "Apple_Bees456$",
                    Port = 1433)



fpax_tbl <- tbl(conn1, "FPAX_MERGED_DETAIL")
clarity_ser_tbl <- tbl(conn2, "CLARITY_SER")
clarity_ser_2_tbl <- tbl(conn2, "CLARITY_SER_2")

msx_ip_conn <- tbl(conn3, dbplyr::ident_q('"MSX"."MSX_IP_OUTPUT"'))
msx_op_conn <- tbl(conn3, dbplyr::ident_q('"MSX"."MSX_OP_OUTPUT"'))

```


```{r FPAX Data Processing}

fpax_data <- fpax_tbl %>%
  filter(SERVICE_YEAR >= 2023) %>%
  filter(is.na(FPSC_DEPARTMENT_DESC) | FPSC_DEPARTMENT_DESC != "UNKNOWN DEPT") %>%
  group_by(SERVICE_YEAR, NPI, MD_NAME, SERVICE_SITE_DESC, CPT_CATEGORY, MRN, CUR_MRN, SERVICE_DATE) %>%
  summarise(UNIT_NUM = sum(UNIT_NUM, na.rm = T),
            WRVU_NUM = sum(WRVU_NUM, na.rm = T),
            CALC_PAYMENT_AMT = sum(CALC_PAYMENT_AMT, na.rm = T)) %>%
  group_by(NPI) %>%
  mutate(total_payments = sum(CALC_PAYMENT_AMT, na.rm = T)) %>%
  filter(total_payments > 0) %>%
  dplyr::select(-total_payments) %>%
  collect()

fpax_data_summary <- fpax_data %>%
  # mutate(SERVICE_SITE_DESC_GRP = case_when(str_detect(SERVICE_SITE_DESC, "Emergency") ~ "ER",
  #                                          str_detect(SERVICE_SITE_DESC, "Outpatient") ~ "Outpatient Hospital",
  #                                          str_detect(SERVICE_SITE_DESC, "Office") ~ "Office",
  #                                          str_detect(SERVICE_SITE_DESC, "Inpatient") & str_detect(SERVICE_SITE_DESC, "Inpatient") ~ "Inpatient",
  #                                          TRUE ~ "Other Place of Service")) %>%
  mutate(SERVICE_SITE_DESC_CPT_GRP = case_when(str_detect(SERVICE_SITE_DESC, "Emergency") ~ "ER",
                                           str_detect(SERVICE_SITE_DESC, "Outpatient") ~ "Hospital Outpatient",
                                           str_detect(SERVICE_SITE_DESC, "Office") ~ "Office",
                                           str_detect(SERVICE_SITE_DESC, "Inpatient") & str_detect(CPT_CATEGORY, "SURGERY") ~ "Inpatient-Surgery",
                                           str_detect(SERVICE_SITE_DESC, "Inpatient") & !str_detect(CPT_CATEGORY, "SURGER") ~ "Inpatient",
                                           TRUE ~ "Other Place of Service")) %>%
  group_by(NPI, MD_NAME, SERVICE_SITE_DESC_CPT_GRP, SERVICE_YEAR, MRN, CUR_MRN, SERVICE_DATE) %>%
  summarise(UNIT_NUM = sum(UNIT_NUM, na.rm = T),
            WRVU_NUM = sum(WRVU_NUM, na.rm = T),
            CALC_PAYMENT_AMT = sum(CALC_PAYMENT_AMT, na.rm = T))


```


```{r MSX Data}

total_dsch <- msx_ip_conn %>%
  filter(FISCAL_YR_MSX >= 2023) %>%
  filter(TOTAL_CHARGES_MSX > 0) %>% 
  group_by(MSMRN, CUR_MRN, ADMIT_DT_SRC, DSCH_DT_SRC) %>%
  summarise(discharge = 1) %>%
  collect()


total_case <- msx_ip_conn %>%
  filter(FISCAL_YR_MSX >= 2023) %>%
  filter(TOTAL_CHARGES_MSX > 0) %>% 
  filter(LVL1_SURGERY_SRC >0 | LVL1_TRANSPLANT_SRC >0) %>%
  group_by(MSMRN, CUR_MRN, ADMIT_DT_SRC, DSCH_DT_SRC) %>%
  summarise(case = 1) %>%
  collect()

total_ip <- merge(total_dsch, total_case, all = T)

total_ip_merged <- total_ip %>%
  filter(!is.na(CUR_MRN)) %>%
  mutate(ADMIT_DT_SRC = as.Date(ADMIT_DT_SRC),
         DSCH_DT_SRC = as.Date(DSCH_DT_SRC)) %>%
  mutate(unique_IP_ID = paste0(CUR_MRN, ADMIT_DT_SRC, DSCH_DT_SRC))

```


```{r MSX and FPAX Merged}

msx_fpax_merged <- merge(fpax_data_summary, total_ip_merged, 
                         by = c("CUR_MRN"), all = TRUE)

msx_fpax_merged <- msx_fpax_merged %>%
  mutate(SERVICE_DATE = as.Date(SERVICE_DATE)) %>%
  filter(SERVICE_DATE < as.Date("2024-12-01")) %>%
  mutate(total_dsch_vol = case_when(discharge == 1 & str_detect(SERVICE_SITE_DESC_CPT_GRP, "Inpatient") & between(SERVICE_DATE, ADMIT_DT_SRC, DSCH_DT_SRC) ~ 1,
                                    TRUE ~ 0),
         total_case_vol = case_when(case == 1 & str_detect(SERVICE_SITE_DESC_CPT_GRP, "Inpatient-Surgery") & between(SERVICE_DATE, ADMIT_DT_SRC, DSCH_DT_SRC) ~ 1,
                                    TRUE ~ 0)) %>%
  ungroup() %>%
  group_by(unique_IP_ID) %>%
  mutate(total_cosurgeon_case = case_when(total_case_vol == 1 ~ n_distinct(NPI[total_case_vol==1]),
                                          TRUE ~ 0))


# Count Total Discharges and Cases
msx_fpax_merged_summary <- msx_fpax_merged %>%
  group_by(NPI, MD_NAME, SERVICE_YEAR, SERVICE_SITE_DESC_CPT_GRP) %>% 
  summarise(UNIT_NUM = sum(UNIT_NUM, na.rm = T),
            WRVU_NUM = sum(WRVU_NUM, na.rm = T),
            CALC_PAYMENT_AMT = sum(CALC_PAYMENT_AMT, na.rm = T),
            DISTINCT_MRN_SERVICEDT = n_distinct(MRN, SERVICE_DATE),
            DISTINCT_DISCHARGES = n_distinct(unique_IP_ID[total_dsch_vol==1]),
            DISTINCT_CASES = n_distinct(unique_IP_ID[total_case_vol==1]),
            DISTINCT_COSURGEON_CASES = n_distinct(unique_IP_ID[total_cosurgeon_case>1]))
         

require(openxlsx)
write.xlsx(msx_fpax_merged_summary, "Physician Paymnts, WRVUs, Discharges Jan23_Nov24.xlsx")




msx_fpax_merged_check <- msx_fpax_merged %>%
  filter(NPI == "1003014267")

msx_fpax_merged_summary_check <- msx_fpax_merged_summary %>%
  filter(NPI == "1003014267")

data_list <- list("msx_fpax_merged" = msx_fpax_merged_check,
                  "msx_fpax_merged_summary" = msx_fpax_merged_summary_check)

write.xlsx(data_list, "MSX_FPAX_Audit.xlsx")

```


